Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-07-21 Paper/paper.tex
Margin change
Boom goes the dynamite.

\geometry{verbose,nohead,tmargin=1.25in,bmargin=1in,lmargin=1.5in,rmargin=1.3in}

@@

% A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications, Developing A Workflow for new Web Developers, 
\title{Creating a Testing Framework and Workflow for Developers New to Web Application Engineering} %\vfill gives us the black space at the top of the page
\author{Taggart Ashby}
\degreemonth{June} \degreeyear{2014} \degree{Master of Science}
\defensemonth{June} \defenseyear{2014}
\numberofmembers{3} \chair{Michael Haungs, Ph.D.} \othermemberA{Franz Kurfess, Ph.D.} \othermemberB{David Janzen, Ph.D.} \field{Computer Science} \campus{San Luis Obispo}
\copyrightyears{seven}

@@

@@

An important part of being a RESTful API is that any change to a web page or element is done through a hypertext link and all actions on an element share a single URI. For example, all updates to ``entity1'' are done through ``http://myrestapi.com/entities/entity1'' using the various HTTP methods that can be called using hypertext links on the page. Compare this to a different way to handle that functionality such as ``http://myrestapi.com/entities/UpdateEntity'' where the HTTP request contains information regarding the entity to update. This method handles all updates, regardless of which entity is changing, through a single URI.

@@

Jenkins is a series of web pages that are set up to run on a given server. This is what Jenkins looks like:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}
\end{Figure}
Most companies give Jenkins a sub-domain on their web pages.

@@

MagnumCI offers support for Ruby, PHP, Node.JS, and Go. MagnumCI, much like Semaphore, will attempt to auto-detect commands that it should run based on the project structure and language. All settings are able to be overridden in a yml file.

@@

Where MagnumCI shines is in support of different repositories. MagnumCI offers support for pulling from GitHub, BitBucket, GitLab, and a few others. It does require a bit more setup to get repositories connected, but what it comes down to is a couple lines of copied and pasted text within the repositories' settings.

Right now MagnumCI offers impressive features, private repositories, and extensive repository sources, all for free. It is hard to say that MagnumCI is the best because those features may end up costing money soon after this paper is completed. It is included in this review because it seems to be an up and comer that could prove quite strong.

>>>>

\geometry{verbose,nohead,tmargin=1in,bmargin=1in,lmargin=1.5in,rmargin=1in}

@@

% A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications, Developing A Workflow for new Web Developers, 
\title{Creating a Testing Framework and Workflow for Developers New to Web Application Engineering} %\vfill gives us the black space at the top of the page
\author{Taggart Ashby}
\degreemonth{June} \degreeyear{2014} \degree{Master of Science}
\defensemonth{June} \defenseyear{2014}
\numberofmembers{3} \chair{Michael Haungs, Ph.D.\newline Professor of Computer Science} \othermemberA{Franz Kurfess, Ph.D.\newline Professor of Computer Science} \othermemberB{David Janzen, Ph.D.\newline Professor of Computer Science} \field{Computer Science} \campus{San Luis Obispo}
\copyrightyears{seven}

@@

\listoftables
\listoffigures

@@

An important part of being a RESTful API is that any change to a web page or element is done through a hypertext link and all actions on an element share a single URI. For example, all updates to ``entity1'' are done through ``http://myrestapi.com/entities/ entity1'' using the various HTTP methods that can be called using hypertext links on the page. Compare this to a different way to handle that functionality such as ``http://myrestapi.com/entities/UpdateEntity'' where the HTTP request contains information regarding the entity to update. This method handles all updates, regardless of which entity is changing, through a single URI.

@@

Jenkins is a series of web pages that are set up to run on a given server. This is what Jenkins looks like:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}
  \captionof{figure}{Jenkins main screen}
\end{Figure}
Most companies give Jenkins a sub-domain on their web pages.

@@

MagnumCI offers support for Ruby, PHP, Node.JS, and Go. MagnumCI, much like Semaphore, will attempt to auto-detect commands that it should run based on the project structure and language. All settings are able to be overridden in a file.

@@

MagnumCI offers support for pulling from GitHub, BitBucket, GitLab, and a few others. It does require a bit more setup to get repositories connected, but what it comes down to is a couple lines of copied and pasted text within the repositories' settings.

Right now MagnumCI offers impressive features, private repositories, and extensive repository sources, all for free. It is hard to say that MagnumCI is the best because those features may end up costing money soon after this paper is completed.
